They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-12 paper.tex
Paper: add hyperparameters section

\section{Background}
In \tavs, we utilize a basic genetic algorithm to train a recurrent neural network generated using the Neuroevolution of Augmenting Topologies (NEAT) method and \href{https://www.heatonresearch.com/encog/}{Encog} framework, which can be found \href{https://sharpneat.sourceforge.net/}{here}, which is a generalized deep-learning library that includes implementations of NEAT and HyperNEAT.

@@

\subsection{Code overview}
\subsubsection{PolarVector}
The PolarVector class encapsulates the internal representation that we use for storing and passing vectors to the neural net, as well as keeping track of the previous direction a Zombunny was headed during the previous tick. The PolarVector class essentially wraps a float, direction (in degrees) and a float, magnitude, which provides sufficient information to create a new vector in two-dimensional space. The PolarVector class provides some convenient helper methods for converting between Cartesian and Polar coordinate systems, as the Unity engine primarily uses Cartesian coordinates.

>>>>

\section{Background}
In \tavs, we utilize a basic genetic algorithm to train a recurrent neural
network generated using the Neuroevolution of Augmenting Topologies (NEAT)
method (implemented in the \href{https://www.heatonresearch.com/encog/}{Encog}
framework), which can be found \href{https://sharpneat.sourceforge.net/}{here},
which is a generalized deep-learning library that includes implementations of
a large number of NEAT and HyperNEAT.

@@

\subsection{Code overview}
\subsubsection{Hyperparameters}
The hyperparameters relevant to playing with how the games are the constants at
the top of \path{Assets/Scripts/Evolution/Genome.cs}, \texttt{HEALTH_SCALE},
\texttt{DAMAGE_SCALE}, and \texttt{MOVEMENT_SCALE}; and at the top of
\path{Assets/Scripts/TowerDefence/Level/GenomeManager.cs}, with
\texttt{POPULATION_SIZE}, \texttt{MUTATION_RATE}, \texttt{GROWTH_RATE},
\texttt{SPAWN_DELAY}, and \texttt{STARTING_TOTAL}. The scale constants in
\path{Genome.cs} change how health, speed, and damage are scaled relative to
each other. \texttt{POPULATION_SIZE} represents the number of genomes (and
therefore zombunnies) in every generation. \texttt{MUTATION_RATE} determines how
much variance there is in everey mutation operation. \texttt{GROWTH_RATE}
Determines how much combined speed, health, and damage is available to be
distributed. \texttt{SPAWN_DELAY} determines how much time passes between spawns
in waves. \texttt{STARTING_TOTAL} determines the total number of stats available
to the zombunnies at the start of the game.

\subsubsection{PolarVector}
The PolarVector class encapsulates the internal representation that we use for storing and passing vectors to the neural net, as well as keeping track of the previous direction a Zombunny was headed during the previous tick. The PolarVector class essentially wraps a float, direction (in degrees) and a float, magnitude, which provides sufficient information to create a new vector in two-dimensional space. The PolarVector class provides some convenient helper methods for converting between Cartesian and Polar coordinate systems, as the Unity engine primarily uses Cartesian coordinates.
